Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2015-07-19 doc/GMP2015/revision_3/s08_conclusion.tex
Made a talk, consolidated doc/img, began new revision, updated doc todo and .gitignore

We have also described a novel method of efficiently realizing a 2D qusecs from the optimal DR-plan by modifying the otherwise indecomposable systems  at nodes of a DR-plan. These results rely on a recent theory of Convex Cayley Configuration spaces. Relationships and reductions between these and previously studied problems were formally clarified.

@@

\begin{conjecture}
\label{conj:mfaisoptimal}
    The Modified Frontier Algorithm (MFA)~\cite{lomonosov2004graph} finds a canonical, and hence optimal, DR-plan.
\end{conjecture}

@@

\begin{openproblem}
\label{open:sparsitymatroid}
Although generic rigidity is a property of graphs, and moreover,  in the case of qusecs, generic rigidity has a combinatorial sparsity and tightness-based characterization, the original definition of independence in the rigidity matroid requires an algebraic notion of independence of vectors of indeterminates over $\mathbf{R}$). Thus the definition of the DR-plan requires algebra over the reals.
In fact, the recursive decomposition problem is not tied to geometric constraint graphs or
an algebraic-geometric or mechanical notion of rigidity, and can be defined for any graph using
the notion of an abstract rigidity matroid \cite{graver93book}. This is  type of matroid with two additional matroid axioms,  abstract rigidity matroids can be defined in a purely graph-theoretic manner,  with no need for algebra in their definition. However, such abstract rigidity need not have a sparsity characterization. On the other hand, there are sparsity matroids that do not correspond to any notion of abstract rigidity.
However, when an abstract rigidity matroid is also a sparsity matroid, then the techniques of this
paper  directly apply and we can obtain purely combinatorially defined recursive decompositions of graphs.
\end{openproblem}

@@

\begin{openproblem}
    For fixed $k$, we have polynomial time optimal DR-planning (Section~\ref{sec:DRP}), recombination (modification) in the presence of $k$ overconstraints, optimal modification for decomposition {\sl OMD}$_k(G)$, when at most $k$ constraints are removed (Section~\ref{sec:recomb}) and also optimal completion using at most $k\le 2$ constraints in the body-pin and triangle-multipin cases for a somewhat different optimization of the DR-plan (Section~\ref{sec:table}). However, in the running time of all of these algorithms, $k$ appears in the exponent.  Can $k$ be removed from the exponent?
\end{openproblem}

@@

    The same holds for the restricted OMD problem where the isostatic completion is required to be a tree-decomposable graph of low Cayley complexity (i.e, have special, small DR-plans). One potential obstacle to an indecomposable graph $G$'s membership in the restricted OMD$_k$ for small $k$ is if $G$ is tri-connected and has large girth. In fact, 6-connected (hence rigid) graphs with arbitrarily large girth have been constructed in \cite{servatius2000rigidity}.
\end{openproblem}

The next is the reverse direction of Observation \ref{obs:OC_to_OMD} in Section \ref{sec:table}.
\begin{openproblem}
    Is the OMD (optimal modification for decomposition) problem reducible to the OC (Optimal completion) problem?
\end{openproblem}

@@

\begin{openproblem}
    The pinned line incidence structures of Section \ref{sec:pinnedline}, for example in the case of collagen microfibrils, whose function is elastic contraction, should be considered congruent under projective transformations. I.e, the projective group should be factored out as a trivial motion in a new project for extending the combinatorial rigidity characterization of such systems. (Currently we permit no trivial motions at all).
\end{openproblem}

>>>>

We have also described a novel method of efficiently realizing a 2D qusecs from the optimal DR-plan by modifying the otherwise indecomposable systems  at nodes of a DR-plan. These results rely on a recent theory of convex Cayley configuration spaces. Relationships and reductions between these and previously studied problems were formally clarified.

@@

\begin{conjecture}
\label{conj:mfaisoptimal}
    The Modified \frontier\ Algorithm (MFA)~\cite{lomonosov2004graph} finds a canonical, and hence optimal, DR-plan.
\end{conjecture}

@@

\begin{openproblem}
\label{open:sparsitymatroid}
Although generic rigidity is a property of graphs, and moreover,  in the case of qusecs, generic rigidity has a combinatorial sparsity and tightness-based characterization, the original definition of independence in the rigidity matroid requires an algebraic notion of independence of vectors of indeterminates over $\RR$. Thus the definition of the DR-plan requires algebra over the reals.
In fact, the recursive decomposition problem is not tied to geometric constraint graphs or an algebraic-geometric or mechanical notion of rigidity, and can be defined for any graph using the notion of an abstract rigidity matroid~\cite{graver93book}. This is a type of matroid with two additional matroid axioms; abstract rigidity matroids can be defined in a purely graph-theoretic manner,  with no need for algebra in their definition. However, such abstract rigidity need not have a sparsity characterization. On the other hand, there are sparsity matroids that do not correspond to any notion of abstract rigidity.
However, when an abstract rigidity matroid is also a sparsity matroid, then the techniques of this paper directly apply and we can obtain purely combinatorially defined recursive decompositions of graphs.
\end{openproblem}

@@

\begin{openproblem}
    For fixed $k$, we have
    %
    polynomial time optimal DR-planning (Section~\ref{sec:DRP}),
    %
    recombination (modification) in the presence of $k$ overconstraints,
    %
    optimal modification for decomposition OMD$_k(G)$ when at most $k$ constraints are removed (Section~\ref{sec:recomb}),
    %
    and also optimal completion using at most $k\le 2$ constraints in the body-pin and triangle-multipin cases for a somewhat different optimization of the DR-plan (Section~\ref{sec:table}).
    %
    However, in the running time of all of these algorithms, $k$ appears in the exponent. Can $k$ be removed from the exponent?
\end{openproblem}

@@

    The same holds for the restricted OMD problem where the isostatic completion is required to be a tree-decomposable graph of low Cayley complexity (i.e.\ have special, small DR-plans). One potential obstacle to an indecomposable graph $G$'s membership in the restricted OMD$_k$ for small $k$ is if $G$ is tri-connected and has large girth. In fact, 6-connected (hence rigid) graphs with arbitrarily large girth have been constructed in \cite{servatius2000rigidity}.
\end{openproblem}

The next is the reverse direction of Observation \ref{obs:OC_to_OMD} in Section \ref{sec:table}.
\begin{openproblem}
    Is the OMD (optimal modification for decomposition) problem reducible to the OC (optimal completion) problem?
\end{openproblem}

@@

\begin{openproblem}
    The pinned line incidence structures of Section \ref{sec:pinnedline}, for example in the case of collagen microfibrils, whose function is elastic contraction, should be considered congruent under projective transformations. I.e.\ the projective group should be factored out as a trivial motion in a new project for extending the combinatorial rigidity characterization of such systems. (Currently we permit no trivial motions at all).
\end{openproblem}
